There once was a grid at ol' Carkeek

### 2016-04-05 Manuscript/v0.0/carkeek_grid.tex
describe rarefaction
add total number of reads
note removal of outlier PCr

%To infer a general estimate of the rate of cross-sample contamination likely to be associated with lab procedures, we calculated the proportion of reads containing primer index sequences (or combinations thereof?) that we did not actually use
%
%RESULTS
%Reads were of generally high-quality, with ?(96.48)? % of base calls having a 0.001 or lower probability of incorrect base call (Phred q-score of 30 or higher).
%
%
%Total sequencing clusters passing filter per read:
%
%reads, reads passing filter, % >= Q30, for each run ( 7,052,307 ; 6,752,829; 97.47 :: 7,052,307 ; 6,752,829 ; 95.50)
%
%Cluster density of 358 \UTF{00EF}\UTF{00BF}\UTF{0153}22	clusters per mm^2
%
%XXX % of reads aligned to the PhiX genome
%(31.02 \UTF{00EF}\UTF{00BF}\UTF{0153}0.59	; 29.17 \UTF{00EF}\UTF{00BF}\UTF{0153}0.89)
%
%and error rate as determined from alignment of PhiX reads to the PhiX genome was low (Read 1: 1.26 \UTF{00EF}\UTF{00BF}\UTF{0153}0.07; Read 2: 1.38 \UTF{00EF}\UTF{00BF}\UTF{0153}0.07)
%----------------------------------------------------------------------------

>>>>

We assessed PCR contamination by evaluating the dissimilarity of replicate PCRs of the same DNA sample, and removed one sample for which the Bray-Curtis dissimilarities between itseld and the other replicates exceeded 0.1 (lib_B_tag_GCGCTC).

%To infer a general estimate of the rate of cross-sample contamination likely to be associated with lab procedures, we calculated the proportion of reads containing primer index sequences (or combinations thereof?) that we did not actually use
%
%RESULTS
%Reads were of generally high-quality, with ?(96.48)? % of base calls having a 0.001 or lower probability of incorrect base call (Phred q-score of 30 or higher).
%
%
%Total sequencing clusters passing filter per read: 371,576,190 on NEXTSEQ
%
% THESE BELOW ARE FROM A MISEQ RUN
%reads, reads passing filter, % >= Q30, for each run ( 7,052,307 ; 6,752,829; 97.47 :: 7,052,307 ; 6,752,829 ; 95.50)
%
%Cluster density of 358 \UTF{00EF}\UTF{00BF}\UTF{0153}22	clusters per mm^2
%
%XXX % of reads aligned to the PhiX genome
%(31.02 \UTF{00EF}\UTF{00BF}\UTF{0153}0.59	; 29.17 \UTF{00EF}\UTF{00BF}\UTF{0153}0.89)
%
%and error rate as determined from alignment of PhiX reads to the PhiX genome was low (Read 1: 1.26 \UTF{00EF}\UTF{00BF}\UTF{0153}0.07; Read 2: 1.38 \UTF{00EF}\UTF{00BF}\UTF{0153}0.07)
%----------------------------------------------------------------------------

To scale the OTU counts, we calculated the minimum number of OTU-assigned reads (as opposed to raw number of reads) found in these samples (130402), multiplied this by within-sample proportional abundance of each OTU, and finally rounded these numbers.
